Backward Population Synthesis: Mapping the Evolutionary History of Gravitational-Wave Progenitors

### 2023-01-20 src/tex/ms.tex
add in discussion of features in the ZAMS mass figure

The correlations between the ZAMS masses are similar to those found by A21 with
the majority of the population preferring primary and secondary masses between
$60$--$90\,M_{\odot}$. However, we also find some ZAMS masses which extend up to
$150\,M_{\odot}$ which is the limit imposed by our assumptions. We explore the
formation scenarios which lead to successful GW150914-like mergers and those
which fail to produce GW150914-like mergers below in
Figure~\ref{fig:compare_fixed_variable}.

>>>>

The correlations between the ZAMS masses are similar to those found by A21 with
the majority of the population preferring primary and secondary masses between
$60$--$90\,M_{\odot}$. However, we also find some ZAMS masses which extend up to
$150\,M_{\odot}$ which is the limit imposed by our assumptions. \textbf{The features in the scatter points of the ZAMS masses, most obvious in the region where $M_1,\rm{ZAMS}\sim 140-150\,M_\odot$, are the outcome of the interplay between the progenitor parameters and hyperparameters. The dominant cause of regions with fewer data points is that fewer binary progenitors produce BBH mergers with chirp masses and mass ratios consistent with GW150914's priors. This is most clearly illustrated for progenitors with primary masses between $142-144\,M_\odot$ and secondary masses below $80\,M_[\odot]$.} We explore the
formation scenarios which lead to successful GW150914-like mergers and those
which fail to produce GW150914-like mergers \textbf{in more detail} below in
Figure~\ref{fig:compare_fixed_variable}.
